### 2019-11-23 paper/introduction.tex
after Andrei's review

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
fissile $^{233}$U inventory to start up new \glspl{MSR}. However, $^{233}$U does not
exist in the Earth's crust and can only be produced from fertile $^{232}$Th in 
specific nuclear facilities. Therefore, we examine alternative fissile
materials to replace the $^{233}$U in the startup fuel
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
cycle transition can be achieved after reaching the doubling
time of $^{233}$U $-$ time required to produce enough amount of $^{233}$U to trigger a
	new SD-TMSR $-$ because in this case, all startup fissile material
is being substituted by newly produced $^{233}$U.

@@

>>>>

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
fissile $^{233}$U inventory to start up new \glspl{MSR}. However, $^{233}$U does not
exist in the Earth's crust and can only be produced from fertile $^{232}$Th in 
specific nuclear facilities. Therefore, we examine alternative fissile
materials to replace the $^{233}$U in the startup fuel
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
cycle transition can be achieved after reaching the doubling
time of $^{233}$U (required time to produce enough $^{233}$U to start up a new unit) because in this case, all startup fissile material
is being substituted by newly produced $^{233}$U.

@@

$^{233}$U (in the \texttt{Pa-decay tank}) is contaminated with $^{232}$U, which produced from parasitic (n, 2n) reactions on $^{233}$U itself, or on $^{233}$Pa, or on $^{232}$Th. $^{208}$Tl a daughter of $^{232}$U emits intense $\gamma$-radiation and this makes $^{233}$U difficult to handle. Moreover, for nonproliferation reasons, $^{233}$U could be diluted with $^{238}$U which makes it impossible to use for nuclear weapons.

### 2019-11-23 paper/methods.tex
after Andrei's review

\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
	SD-TMSR.}
	\label{fig:ff}
\end{figure}

@@

\section{Feed and extraction rates} \label{Feed-and-extraction-rates}
In the present work, two different feed mechanisms are used: (1) thorium and (2) non-thorium.
The first mechanism allows continuous feed flow of thorium from the external stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}. In contrast, the second mechanism 
continuously injects external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}) and simultaneously feeds  
all or part of produced $^{233}$U from the \texttt{Pa-decay tank}. The fission 
products (FPs) act as poisons in MSRs: they negatively impact the reactivity. 
Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
$T_{r}$ as the time during which the total fuel salt is reprocessed and 
$dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that 
the \gls{MSR} extracts during time $dt$, thus \cite{nuttin2005potential}

\begin{equation}
\label{Equ:1}
\dfrac{dN_{e}}{dt} = N_{e}\dfrac{\varepsilon_{e}}{T_{r}},	
\end{equation}

where $\varepsilon_{e}$ is the removal efficiency \%. Integration of equation \ref{Equ:1} gives 
the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
is removed), where $\lambda_{e}=\dfrac{{\varepsilon_{e}}}{{T}_{r}}$. The removal constant 
$\lambda_{e}$ of gaseous and other fission products is precisely calculated 
and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
the gaseous \gls{FPs} and non-dissolved metals was set to 30 s (removal 
constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
extracted promptly and continuously via a gas removal system. In contrast, 
chemical processes (i.e. fluorination and reduction) extract the soluble \gls{FPs}, lanthanides, and Pa.
Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
present work, the effective extraction time for soluble \gls{FPs} is 
$\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
equivalent to a chemical reprocessing rate of 5 m$^3$/d chosen by Nuttin \emph{et al.} \cite{nuttin2005potential} and Li \emph{et al.} \cite{li_optimization_2018}. The effective feed rates of 
the heavy metals (HM) are changed during reactor operation to conserve the 
total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9}, and \ref{tab:table10} in \ref{Appendix}.

>>>>

\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
	SD-TMSR \cite{ashraf2019whole_core}.}
	\label{fig:ff}
\end{figure}

@@

\section{Feed and extraction rates} \label{Feed-and-extraction-rates}
In the present work, two different feed mechanisms are used: (1) thorium and (2) non-thorium.
The first mechanism allows continuous feed flow of thorium from the external stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}. In contrast, the second mechanism 
continuously injects external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}) and simultaneously feeds  
all or part of produced $^{233}$U from the \texttt{Pa-decay tank}. The fission 
products (FPs) act as poisons in nuclear reactors: they negatively impact the reactivity. 
Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
the \gls{MSR} extracts $dN_{e}$ amount of particular element $e$ during time $dt$, thus \cite{nuttin2005potential}:
\begin{align}
\dfrac{dN_{e}}{dt} &= N_{e}\dfrac{\varepsilon_{e}}{T_{r}}
\label{Equ:1}
\intertext{where}
dN_{e} 	&= \mbox{the amount of particular element $e$} \nonumber \\
dt   	&= \mbox{the extraction time of $dN_e$} \nonumber \\
N_{e}  	&= \mbox{total inventory of element $e$} \nonumber \\
\varepsilon_{e}	&= \mbox{the removal efficiency $\%$} \nonumber \\
T_{r}	&= \mbox{the time during which the total fuel salt is reprocessed.} \nonumber
\end{align}

Integration of equation \ref{Equ:1} gives the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
is removed), where $\lambda_{e}=\dfrac{{\varepsilon_{e}}}{{T}_{r}}$. The removal constant 
$\lambda_{e}$ of gaseous and other fission products is precisely calculated 
and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
the gaseous \gls{FPs} and non-dissolved metals was set to 30 s (removal 
constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
extracted promptly and continuously via a gas removal system. In contrast, 
chemical processes (i.e. fluorination and reduction) extract the soluble \gls{FPs}, lanthanides, and Pa.
Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
present work, the effective extraction time for soluble \gls{FPs} is 
$\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
equivalent to a chemical reprocessing rate of 5 m$^3$/d chosen by Nuttin \emph{et al.} \cite{nuttin2005potential} and Li \emph{et al.} \cite{li_optimization_2018}. The effective feed rates of 
the heavy metals (HM) are changed during reactor operation to conserve the 
total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9}, and \ref{tab:table10} in \ref{Appendix}.
